---
title: "task1"
author: "許煌浚"
date: "2019/7/11"
output: html_document
---

```{r}
library(stats)
library(base)
library(dplyr)
library(ggplot2)
library(ggfortify)
library(tidyr)
library(magrittr)
a=c()
i=1979
while(i<2016){
  a<-append(a, toString(i), after = length(a))
  i=i+1
}
filename1 <- "Unemployment Rate by Year Since 1929 Compared to Inflation and GDP.csv"
data1<-read.csv(filename1)
```

# Data1-Unemployment Rate by Year Since 1929 Compared to Inflation and GDP:https://www.thebalance.com/unemployment-rate-by-year-3305506

```{r}
knitr::kable(data1,format = 'html')
```

```{r}
data2<-data1%>%filter(data1$Year%in%a)
```

# Only Select Data During 1979-2015

```{r}
knitr::kable(data2,format = 'html')
```

```{r}
filename2 <- "who_suicide_statistics.csv"
data3<-read.csv(filename2)
```

# Data2-WHO Suicide Statistics:https://www.kaggle.com/szamil/who-suicide-statistics

```{r}
knitr::kable(data3,format='html')
```

# Only Select Data Of US And During 1979-2015

```{r}
data4<-data3%>%filter(country=="United States of America",data3$year%in%a)
```

```{r}
knitr::kable(data4,format='html')
```

# Calculate Suicide Rate By Adding Number Of Suicide Then Divided By Population

```{r}
data5<-aggregate(data4$suicides_no, by=list(Category=data4$year), FUN=sum)/aggregate(data4$population, by=list(Category=data4$year), FUN=sum)
```

```{r}
knitr::kable(data5,format='html')
```

# Combine The Two Dataframes

```{r}
final<-data2%>%mutate(suicide_rate=data5$x)
colnames(final)=c("year","Unemployment_Rate","GDP","Inflation","What_Happened","suicide_rate")
```

```{r}
knitr::kable(final,format='html')
```

# Plot US's Suicide Rate Versus Years

```{r}
ggplot(data = final, aes(x = year, y=suicide_rate)) +
  geom_point()
```

# Plot US's Suicide Rate Versus Unemployment_Rate 

```{r}
final %>%
  ggplot(aes(x=Unemployment_Rate, y=suicide_rate)) +
  geom_point(aes(col=Unemployment_Rate), position=position_jitter(width=.05)) +
  geom_smooth(method='lm',formula=y~x, se=F)
```

# Calculate The Correlation Coefficient Of Suicide Rate And Unemployment_Rate 

```{r}
sprintf("Correlation Coefficient=%.4f",cor(final$Unemployment_Rate,final$suicide_rate))
```

# Crawler

```{r setup, include=FALSE}
source('pttTestFunction.R')
id = c(3475:3479)
URL = paste0("https://www.ptt.cc/bbs/Tech_Job/index", id, ".html")
filename = paste0(id, ".txt")
pttTestFunction(URL[1], filename[1])
mapply(pttTestFunction, 
       URL = URL, filename = filename)
```

```{r}
rm(list=ls(all.names = TRUE))
library(NLP)
library(tm)
library(jiebaRD)
library(jiebaR)
library(RColorBrewer)
library(wordcloud)
filenames <- list.files(getwd(), pattern="*.txt")
files <- lapply(filenames, readLines)
docs <- Corpus(VectorSource(files))
#移除可能有問題的符號
toSpace <- content_transformer(function(x, pattern) {
  return (gsub(pattern, " ", x))
}
)
docs <- tm_map(docs, toSpace, "※")
docs <- tm_map(docs, toSpace, "◆")
docs <- tm_map(docs, toSpace, "‧")
docs <- tm_map(docs, toSpace, "的")
docs <- tm_map(docs, toSpace, "我")
docs <- tm_map(docs, toSpace, "是")
docs <- tm_map(docs, toSpace, "推")
docs <- tm_map(docs, toSpace, "噓")
docs <- tm_map(docs, toSpace, "幣")
docs <- tm_map(docs, toSpace, "就")
docs <- tm_map(docs, toSpace, "有")
docs <- tm_map(docs, toSpace, "也")
docs <- tm_map(docs, toSpace, "都")
docs <- tm_map(docs, toSpace, "不")
docs <- tm_map(docs, toSpace, "是")
docs <- tm_map(docs, toSpace, "在")
docs <- tm_map(docs, toSpace, "沒")
docs <- tm_map(docs, toSpace, "看")
docs <- tm_map(docs, toSpace, "很")
docs <- tm_map(docs, toSpace, "你")
docs <- tm_map(docs, toSpace, "啦")
docs <- tm_map(docs, toSpace, "要")
docs <- tm_map(docs, toSpace, "啊")
docs <- tm_map(docs, toSpace, "被")
docs <- tm_map(docs, toSpace, "但")
docs <- tm_map(docs, toSpace, "跟")
docs <- tm_map(docs, toSpace, "嗎")
docs <- tm_map(docs, toSpace, "吧")
docs <- tm_map(docs, toSpace, "買")
docs <- tm_map(docs, toSpace, "會")
docs <- tm_map(docs, toSpace, "好")
docs <- tm_map(docs, toSpace, "還")
docs <- tm_map(docs, toSpace, "獲得")
docs <- tm_map(docs, toSpace, "恭喜")
docs <- tm_map(docs, toSpace, "看板")
docs <- tm_map(docs, toSpace, "作者")
docs <- tm_map(docs, toSpace, "發信站")
docs <- tm_map(docs, toSpace, "批踢踢實業坊")
docs <- tm_map(docs, toSpace, "[a-zA-Z]")
docs <- tm_map(docs, toSpace, "了")
docs <- tm_map(docs, toSpace, "所以")
docs <- tm_map(docs, toSpace, "可能")
docs <- tm_map(docs, toSpace, "自己")
docs <- tm_map(docs, toSpace, "什麼")
docs <- tm_map(docs, toSpace, "知道")
docs <- tm_map(docs, toSpace, "他們")
docs <- tm_map(docs, toSpace, "如果")
docs <- tm_map(docs, toSpace, "時間")
docs <- tm_map(docs, toSpace, "文章")
docs <- tm_map(docs, toSpace, "做")
docs <- tm_map(docs, toSpace, "怎麼")
docs <- tm_map(docs, toSpace, "大家")
docs <- tm_map(docs, toSpace, "只")
docs <- tm_map(docs, toSpace, "臺灣")
docs <- tm_map(docs, toSpace, "與")
docs <- tm_map(docs, toSpace, "當")
docs <- tm_map(docs, toSpace, "因為")
docs <- tm_map(docs, toSpace, "應該")
docs <- tm_map(docs, toSpace, "比較")
docs <- tm_map(docs, toSpace, "來自")
docs <- tm_map(docs, toSpace, "可以")
docs <- tm_map(docs, toSpace, "問題")
docs <- tm_map(docs, toSpace, "來")
docs <- tm_map(docs, toSpace, "台灣")
docs <- tm_map(docs, toSpace, "人")
docs <- tm_map(docs, toSpace, "到")
docs <- tm_map(docs, toSpace, "多")
docs <- tm_map(docs, toSpace, "說")
docs <- tm_map(docs, toSpace, "真")
docs <- tm_map(docs, toSpace, "用")
docs <- tm_map(docs, toSpace, "後")
docs <- tm_map(docs, toSpace, "這")
docs <- tm_map(docs, toSpace, "那")
docs <- tm_map(docs, toSpace, "能")
docs <- tm_map(docs, toSpace, "去")
docs <- tm_map(docs, toSpace, "板")
docs <- tm_map(docs, toSpace, "這樣")
docs <- tm_map(docs, toSpace, "才")
docs <- tm_map(docs, toSpace, "和")
docs <- tm_map(docs, toSpace, "上")
docs <- tm_map(docs, toSpace, "下")
docs <- tm_map(docs, toSpace, "大")
docs <- tm_map(docs, toSpace, "她")
docs <- tm_map(docs, toSpace, "他")
docs <- tm_map(docs, toSpace, "或")
docs <- tm_map(docs, toSpace, "像")
docs <- tm_map(docs, toSpace, "一個")
docs <- tm_map(docs, toSpace, "比")
docs <- tm_map(docs, toSpace, "然")
docs <- tm_map(docs, toSpace, "給")
docs <- tm_map(docs, toSpace, "以")
docs <- tm_map(docs, toSpace, "少")
docs <- tm_map(docs, toSpace, "對")
docs <- tm_map(docs, toSpace, "樣")
docs <- tm_map(docs, toSpace, "找")
docs <- tm_map(docs, toSpace, "過")
docs <- tm_map(docs, toSpace, "些")
docs <- tm_map(docs, toSpace, "想")
docs <- tm_map(docs, toSpace, "出")
docs <- tm_map(docs, toSpace, "等")
docs <- tm_map(docs, toSpace, "更")
docs <- tm_map(docs, toSpace, "們")
docs <- tm_map(docs, toSpace, "最")
docs <- tm_map(docs, toSpace, "班")
docs <- tm_map(docs, toSpace, "其")
docs <- tm_map(docs, toSpace, "一")
docs <- tm_map(docs, toSpace, "又")
docs <- tm_map(docs, toSpace, "別")
docs <- tm_map(docs, toSpace, "差")
docs <- tm_map(docs, toSpace, "再")
docs <- tm_map(docs, toSpace, "算")
docs <- tm_map(docs, toSpace, "麼")
docs <- tm_map(docs, toSpace, "標題")
docs <- tm_map(docs, toSpace, "加")
docs <- tm_map(docs, toSpace, "為")
docs <- tm_map(docs, toSpace, "新")
docs <- tm_map(docs, toSpace, "種")
docs <- tm_map(docs, toSpace, "高")
docs <- tm_map(docs, toSpace, "萬")
docs <- tm_map(docs, toSpace, "編輯")
docs <- tm_map(docs, toSpace, "重")
docs <- tm_map(docs, toSpace, "中")
docs <- tm_map(docs, toSpace, "正")
docs <- tm_map(docs, toSpace, "個")
docs <- tm_map(docs, toSpace, "時")
docs <- tm_map(docs, toSpace, "之")
docs <- tm_map(docs, toSpace, "表示")
docs <- tm_map(docs, toSpace, "力")
docs <- tm_map(docs, toSpace, "已經")
docs <- tm_map(docs, toSpace, "得")
docs <- tm_map(docs, toSpace, "事")
docs <- tm_map(docs, toSpace, "堆")
docs <- tm_map(docs, toSpace, "前")
docs <- tm_map(docs, toSpace, "家")
docs <- tm_map(docs, toSpace, "阿")
docs <- tm_map(docs, toSpace, "快")
docs <- tm_map(docs, toSpace, "可")
docs <- tm_map(docs, toSpace, "喔")
docs <- tm_map(docs, toSpace, "走")
docs <- tm_map(docs, toSpace, "覺得")
docs <- tm_map(docs, toSpace, "及")
docs <- tm_map(docs, toSpace, "定")
docs <- tm_map(docs, toSpace, "樓")
docs <- tm_map(docs, toSpace, "而")
docs <- tm_map(docs, toSpace, "文")
docs <- tm_map(docs, toSpace, "幫")
docs <- tm_map(docs, toSpace, "拿")
docs <- tm_map(docs, toSpace, "歲")
docs <- tm_map(docs, toSpace, "專")
docs <- tm_map(docs, toSpace, "應")
docs <- tm_map(docs, toSpace, "讓")
docs <- tm_map(docs, toSpace, "法")
docs <- tm_map(docs, toSpace, "表示")
docs <- tm_map(docs, toSpace, "進")
docs <- tm_map(docs, toSpace, "把")
docs <- tm_map(docs, toSpace, "常")
docs <- tm_map(docs, toSpace, "從")
docs <- tm_map(docs, toSpace, "生")
docs <- tm_map(docs, toSpace, "讚")
docs <- tm_map(docs, toSpace, "年")
docs <- tm_map(docs, toSpace, "台")
docs <- tm_map(docs, toSpace, "目")
docs <- tm_map(docs, toSpace, "太")
docs <- tm_map(docs, toSpace, "女")
docs <- tm_map(docs, toSpace, "小")
docs <- tm_map(docs, toSpace, "心")
docs <- tm_map(docs, toSpace, "於")
docs <- tm_map(docs, toSpace, "呢")
docs <- tm_map(docs, toSpace, "且")
docs <- tm_map(docs, toSpace, "近")
docs <- tm_map(docs, toSpace, "夠")
docs <- tm_map(docs, toSpace, "越")
docs <- tm_map(docs, toSpace, "次")
docs <- tm_map(docs, toSpace, "面")
docs <- tm_map(docs, toSpace, "實")
docs <- tm_map(docs, toSpace, "同")
docs <- tm_map(docs, toSpace, "已")
docs <- tm_map(docs, toSpace, "成")
docs <- tm_map(docs, toSpace, "覺")
docs <- tm_map(docs, toSpace, "至")
docs <- tm_map(docs, toSpace, "天")
docs <- tm_map(docs, toSpace, "活")
docs <- tm_map(docs, toSpace, "話")
docs <- tm_map(docs, toSpace, "認")
docs <- tm_map(docs, toSpace, "哪")
docs <- tm_map(docs, toSpace, "根本")
docs <- tm_map(docs, toSpace, "決")
docs <- tm_map(docs, toSpace, "每")
docs <- tm_map(docs, toSpace, "通")
docs <- tm_map(docs, toSpace, "男")
docs <- tm_map(docs, toSpace, "三")
docs <- tm_map(docs, toSpace, "分享")
docs <- tm_map(docs, toSpace, "起")
docs <- tm_map(docs, toSpace, "塑")
docs <- tm_map(docs, toSpace, "拜託")
docs <- tm_map(docs, toSpace, "學")
docs <- tm_map(docs, toSpace, "試")
docs <- tm_map(docs, toSpace, "談")
docs <- tm_map(docs, toSpace, "產")
#移除標點符號 (punctuation)
#移除數字 (digits)、空白 (white space)
docs <- tm_map(docs, removePunctuation)
docs <- tm_map(docs, removeNumbers)
docs <- tm_map(docs, stripWhitespace)
docs
```

```{r}
mixseg = worker()
jieba_tokenizer=function(d){
  unlist(segment(d[[1]],mixseg))
}
seg = lapply(docs, jieba_tokenizer)
freqFrame = as.data.frame(table(unlist(seg)))
freqFrame = freqFrame[order(freqFrame$Freq,decreasing=TRUE), ]
library(knitr)
kable(head(freqFrame), format = "markdown")
```

```{r}
wordcloud(freqFrame$Var1,freqFrame$Freq,
          scale=c(5,0.1),min.freq=25,max.words=150,
          random.order=TRUE, random.color=FALSE, 
          rot.per=.1, colors=brewer.pal(8, "Dark2"),
          ordered.colors=FALSE,use.r.layout=FALSE,
          fixed.asp=TRUE)
```














